\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-26 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
Essai de mettre "Model B" centré dans le tableau
Ne marche pas :(
Tableaux appendix  A et B marche avec modèle I
Petits pas sur les tableaux de l’annexe
Progrès sur les tableaux annexe
Inversion des inputs pour les tables de l’appendix
B2-B5 et B7-B10
nouvelles modifs main text et appendix 1

In this section, we report the estimation results of the three models: Model (A) (with only ad-valorem costs), Model (B) (with both additive and ad-valorem) and Model (C) (with only additive costs). Table \ref{tab:3models_estimation_results_air} reports the results for air transport, Table \ref{tab:3models_estimation_results_vessel} for vessel transport.

@@

  \centering
   \footnotesize{
    \caption{Estimation results of the three models (Air, 3-digit level)}
  \label{tab:3models_estimation_results_air}%
    \begin{tabular}{l|c c c c c c c c c}
    \hline \hline
    \textbf{Year} & \multicolumn{1}{c}{\textbf{1974}} & \multicolumn{1}{c}{\textbf{1980}} & \multicolumn{1}{c}{\textbf{1985}} & \multicolumn{1}{c}{\textbf{1990}} & \multicolumn{1}{c}{\textbf{1995}} & \multicolumn{1}{c}{\textbf{2000}} & \multicolumn{1}{c}{\textbf{2005}} & \multicolumn{1}{c}{\textbf{2010}} & \multicolumn{1}{c}{\textbf{2013}} \\ \hline
   $\#$ obs. & \multicolumn{1}{c}{14955} & \multicolumn{1}{c}{16118} & \multicolumn{1}{c}{19908} & \multicolumn{1}{c}{24958} & \multicolumn{1}{c}{31037} & \multicolumn{1}{c}{35027} & \multicolumn{1}{c}{41806} & \multicolumn{1}{c}{40279} & \multicolumn{1}{c}{39351} \\
   $\#$  origin countries & \multicolumn{1}{c}{152} & \multicolumn{1}{c}{165} & \multicolumn{1}{c}{169} & \multicolumn{1}{c}{181} & \multicolumn{1}{c}{207} & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{211} & \multicolumn{1}{c}{210} & \multicolumn{1}{c}{210} \\
   $\#$  sectors & \multicolumn{1}{c}{203} & \multicolumn{1}{c}{204} & \multicolumn{1}{c}{207} & \multicolumn{1}{c}{212} & \multicolumn{1}{c}{217} & \multicolumn{1}{c}{218} & \multicolumn{1}{c}{217} & \multicolumn{1}{c}{216} & \multicolumn{1}{c}{212} \\ \hline
    \multicolumn{10}{l}{\textbf{Model (A) - Iceberg transport costs only} ($\widehat{\tau}^{ice}$)} \\ \hline
    Mean (in \%) & \multicolumn{1}{c}{6.93} & \multicolumn{1}{c}{5.41} & \multicolumn{1}{c}{6.08} & \multicolumn{1}{c}{5.03} & \multicolumn{1}{c}{4.61} & \multicolumn{1}{c}{3.60} & \multicolumn{1}{c}{4.10} & \multicolumn{1}{c}{4.19} & \multicolumn{1}{c}{3.36} \\
    Median (in \%)& \multicolumn{1}{c}{5.43} & \multicolumn{1}{c}{3.79} & \multicolumn{1}{c}{5.47} & \multicolumn{1}{c}{4.37} & \multicolumn{1}{c}{3.80} & \multicolumn{1}{c}{2.47} & \multicolumn{1}{c}{3.12} & \multicolumn{1}{c}{3.41} & \multicolumn{1}{c}{2.92} \\
    Standard Deviation & \multicolumn{1}{c}{0.04} & \multicolumn{1}{c}{0.04} & \multicolumn{1}{c}{0.04} & \multicolumn{1}{c}{0.03} & \multicolumn{1}{c}{0.03} & \multicolumn{1}{c}{0.03} & \multicolumn{1}{c}{0.03} & \multicolumn{1}{c}{0.02} & \multicolumn{1}{c}{0.02} \\ \hline
    \multicolumn{10}{l}{\textbf{Model (B) - With additive and ad-valorem transport costs}} \\ \hline
     \multicolumn{10}{l}{ \textit{Multiplicative term} ($\widehat{\tau}^{adv}$)} \\ \hline
    Mean (in \%) & \multicolumn{1}{c}{3.64} & \multicolumn{1}{c}{2.32} & \multicolumn{1}{c}{2.46} & \multicolumn{1}{c}{2.38} & \multicolumn{1}{c}{2.05} & \multicolumn{1}{c}{1.66} & \multicolumn{1}{c}{2.00} & \multicolumn{1}{c}{2.57} & \multicolumn{1}{c}{1.70} \\
    Median (in \%)& \multicolumn{1}{c}{2.71} & \multicolumn{1}{c}{1.57} & \multicolumn{1}{c}{1.79} & \multicolumn{1}{c}{1.60} & \multicolumn{1}{c}{1.39} & \multicolumn{1}{c}{1.20} & \multicolumn{1}{c}{1.57} & \multicolumn{1}{c}{2.24} & \multicolumn{1}{c}{1.72} \\
    Standard Deviation & \multicolumn{1}{c}{0.03} & \multicolumn{1}{c}{0.02} & \multicolumn{1}{c}{0.02} & \multicolumn{1}{c}{0.02} & \multicolumn{1}{c}{0.02} & \multicolumn{1}{c}{0.02} & \multicolumn{1}{c}{0.02} & \multicolumn{1}{c}{0.02} & \multicolumn{1}{c}{0.01} \\ \hline
      \multicolumn{10}{l}{\textit{Additive term} ($\widehat{t}/\widetilde{p}$)} \\ \hline
    Mean (in \%) & \multicolumn{1}{c}{2.56} & \multicolumn{1}{c}{2.04} & \multicolumn{1}{c}{2.83} & \multicolumn{1}{c}{1.83} & \multicolumn{1}{c}{1.64} & \multicolumn{1}{c}{1.30} & \multicolumn{1}{c}{1.43} & \multicolumn{1}{c}{1.13} & \multicolumn{1}{c}{1.01} \\
    Median (in \%)& \multicolumn{1}{c}{1.13} & \multicolumn{1}{c}{0.54} & \multicolumn{1}{c}{1.30} & \multicolumn{1}{c}{0.84} & \multicolumn{1}{c}{0.68} & \multicolumn{1}{c}{0.45} & \multicolumn{1}{c}{0.53} & \multicolumn{1}{c}{0.43} & \multicolumn{1}{c}{0.47} \\
    Standard Deviation & \multicolumn{1}{c}{0.04} & \multicolumn{1}{c}{0.04} & \multicolumn{1}{c}{0.04} & \multicolumn{1}{c}{0.03} & \multicolumn{1}{c}{0.03} & \multicolumn{1}{c}{0.03} & \multicolumn{1}{c}{0.03} & \multicolumn{1}{c}{0.02} & \multicolumn{1}{c}{0.02} \\ \hline
    \multicolumn{10}{l}{\textbf{Model (C) - With additive transport costs only} ($\widehat{t}^{add}/\widetilde{p}$)} \\ \hline
    Mean (in \%) & \multicolumn{1}{c}{6.88} & \multicolumn{1}{c}{4.82} & \multicolumn{1}{c}{5.99} & \multicolumn{1}{c}{4.44} & \multicolumn{1}{c}{3.80} & \multicolumn{1}{c}{3.09} & \multicolumn{1}{c}{4.00} & \multicolumn{1}{c}{4.49} & \multicolumn{1}{c}{3.29} \\
    Median (in \%)& \multicolumn{1}{c}{4.45} & \multicolumn{1}{c}{1.82} & \multicolumn{1}{c}{3.36} & \multicolumn{1}{c}{2.27} & \multicolumn{1}{c}{1.72} & \multicolumn{1}{c}{1.39} & \multicolumn{1}{c}{1.93} & \multicolumn{1}{c}{2.72} & \multicolumn{1}{c}{2.06} \\
    Standard Deviation & \multicolumn{1}{c}{0.09} & \multicolumn{1}{c}{0.08} & \multicolumn{1}{c}{0.08} & \multicolumn{1}{c}{0.10} & \multicolumn{1}{c}{0.09} & \multicolumn{1}{c}{0.06} & \multicolumn{1}{c}{0.07} & \multicolumn{1}{c}{0.07} & \multicolumn{1}{c}{0.05} \\  \hline \hline
    \end{tabular}
    }
\end{table}%

\begin{table}[htbp]
	\centering
	\footnotesize{
	\caption{Estimation results of the three models (Air, products at 5-digit level, sectors at 3-digit level)}
	\label{tab:3models_estimation_results_air}%
	\input{TableA1_air.tex}
   \begin{tablenotes}
	\tiny
	\item Statistics are weighted by value
	\item \textbf{Model (B): With additive and ad-valorem transport costs}
\end{tablenotes}

@@

\begin{table}[htbp]
  \centering
   \footnotesize{
    \caption{Estimation results of the three models (Vessel, 3-digit level)}
  \label{tab:3models_estimation_results_vessel}%
    \begin{tabular}{l|c c c c c c c c c}
    \hline \hline
    \textbf{Year} & 1974  & 1980  & 1985  & 1990  & 1995  & 2000  & 2005  & 2010  & 2013 \\ \hline
    $\# $obs. & 19007 & 17356 & 23348 & 28383 & 32146 & 36090 & 41319 & 37748 & 38473 \\
    $\#$  origin countries & 154   & 163   & 171   & 179   & 201   & 206   & 206   & 198   & 203 \\
    $\#$  sectors & 239   & 232   & 232   & 232   & 228   & 230   & 231   & 226   & 224 \\ \hline
    \multicolumn{10}{l}{\textbf{Model (A) - Iceberg transport costs only} ($\widehat{\tau}^{ice}$)} \\ \hline
    Mean (in \%) & 9.79  & 6.53  & 6.88  & 5.67  & 5.14  & 5.10  & 5.47  & 3.99  & 3.60 \\
    Median (in \%)& 9.58  & 5.50  & 6.33  & 4.63  & 4.29  & 4.85  & 4.90  & 3.56  & 3.28 \\
    Standard Deviation & 0.05  & 0.04  & 0.04  & 0.03  & 0.03  & 0.03  & 0.03  & 0.02  & 0.02 \\ \hline
    \multicolumn{10}{l}{\textbf{Model (B ) - With additive and ad-valorem transport costs} } \\ \hline
     \multicolumn{10}{l}{\textit{Multiplicative term} ($\widehat{\tau}^{adv}$)} \\ \hline
    Mean (in \%) & 5.42  & 3.08  & 4.02  & 3.31  & 2.79  & 2.49  & 2.68  & 1.95  & 2.22 \\
    Median (in \%) & 4.93  & 2.42  & 3.60  & 2.81  & 2.53  & 2.07  & 2.08  & 1.76  & 1.82 \\
    Standard Deviation & 0.04  & 0.02  & 0.03  & 0.02  & 0.02  & 0.02  & 0.02  & 0.02  & 0.01 \\ \hline
       \multicolumn{10}{l}{\textit{Additive term} ($\widehat{t}/\widetilde{p}$)}  \\ \hline
    Mean (in \%)  & 5.08  & 3.38  & 3.19  & 2.73  & 2.73  & 2.80  & 3.02  & 2.47  & 1.46 \\
    Median (in \%) & 2.94  & 2.27  & 2.06  & 1.70  & 1.82  & 2.19  & 2.16  & 1.89  & 0.76 \\
    Standard Deviation & 0.09  & 0.05  & 0.04  & 0.04  & 0.04  & 0.04  & 0.04  & 0.03  & 0.02 \\ \hline
    \multicolumn{10}{l}{\textbf{Model (C) - With additive transport costs only} ($\widehat{t}^{add}/\widetilde{p}$)} \\ \hline
    Mean (in \%) & 14.51 & 10.05 & 10.47 & 14.62 & 8.37  & 8.02  & 8.41  & 6.40  & 5.23 \\
    Median (in \%)& 9.53  & 6.69  & 7.16  & 6.22  & 4.68  & 4.93  & 5.74  & 3.87  & 3.57 \\
    Standard Deviation & 0.24  & 0.17  & 0.18  & 0.30  & 0.15  & 0.16  & 0.15  & 0.15  & 0.10 \\ \hline \hline
   \end{tabular}%
   }
\end{table}%

\begin{table}[htbp]
	\centering
	\footnotesize{
		\caption{Estimation results of the three models (Vessel, products at 5-digit level, sectors at 3-digit level)}
		\label{tab:3models_estimation_results_ves}%
		\input{TableA1_ves.tex}
		\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\end{tablenotes}
   }
\end{table}%

@@

\begin{landscape}
  \centering
  \footnotesize{
  \caption{Quality-of-fit diagnostic tests of the three models (Air, 3-digit level)}
    \label{tab:3models_diagnosis_air}%
   \begin{tabular}{l|c|c|c|c|c|c|c|c|c}
    \hline \hline
    \textbf{Year} & \multicolumn{1}{c}{\textbf{1974}} & \multicolumn{1}{c}{\textbf{1980}} & \multicolumn{1}{c}{\textbf{1985}} & \multicolumn{1}{c}{\textbf{1990}} & \multicolumn{1}{c}{\textbf{1995}} & \multicolumn{1}{c}{\textbf{2000}} & \multicolumn{1}{c}{\textbf{2005}} & \multicolumn{1}{c}{\textbf{2010}} & \multicolumn{1}{c}{\textbf{2013}} \\ \hline
    \multicolumn{10}{l}{\textbf{$R^2$}} \\ \hline
    Model (A) & \multicolumn{1}{c}{0.297} & \multicolumn{1}{c}{0.267} & \multicolumn{1}{c}{0.302} & \multicolumn{1}{c}{0.251} & \multicolumn{1}{c}{0.142} & \multicolumn{1}{c}{0.318} & \multicolumn{1}{c}{0.460} & \multicolumn{1}{c}{0.421} & \multicolumn{1}{c}{0.313} \\
    Model (B) & \multicolumn{1}{c}{0.594} & \multicolumn{1}{c}{0.646} & \multicolumn{1}{c}{0.635} & \multicolumn{1}{c}{0.627} & \multicolumn{1}{c}{0.658} & \multicolumn{1}{c}{0.640} & \multicolumn{1}{c}{0.593} & \multicolumn{1}{c}{0.513} & \multicolumn{1}{c}{0.419} \\
    Model (C) & \multicolumn{1}{c}{0.489} & \multicolumn{1}{c}{0.543} & \multicolumn{1}{c}{0.531} & \multicolumn{1}{c}{0.517} & \multicolumn{1}{c}{0.546} & \multicolumn{1}{c}{0.518} & \multicolumn{1}{c}{0.464} & \multicolumn{1}{c}{0.339} & \multicolumn{1}{c}{0.295} \\ \hline
    \multicolumn{10}{l}{\textbf{SER}}\\ \hline
    Model (A) & \multicolumn{1}{c}{0.791} & \multicolumn{1}{c}{0.860} & \multicolumn{1}{c}{0.831} & \multicolumn{1}{c}{0.811} & \multicolumn{1}{c}{0.798} & \multicolumn{1}{c}{0.844} & \multicolumn{1}{c}{0.837} & \multicolumn{1}{c}{0.857} & \multicolumn{1}{c}{0.920} \\
    Model (B) & \multicolumn{1}{c}{0.674} & \multicolumn{1}{c}{0.715} & \multicolumn{1}{c}{0.692} & \multicolumn{1}{c}{0.675} & \multicolumn{1}{c}{0.641} & \multicolumn{1}{c}{0.697} & \multicolumn{1}{c}{0.727} & \multicolumn{1}{c}{0.787} & \multicolumn{1}{c}{0.847} \\
    Model (C) & \multicolumn{1}{c}{1.610} & \multicolumn{1}{c}{1.778} & \multicolumn{1}{c}{1.736} & \multicolumn{1}{c}{1.699} & \multicolumn{1}{c}{1.700} & \multicolumn{1}{c}{1.786} & \multicolumn{1}{c}{1.783} & \multicolumn{1}{c}{1.776} & \multicolumn{1}{c}{1.723} \\ \hline
   \multicolumn{10}{l}{ \textbf{AIC criteria}} \\ \hline
    Model (A) & \multicolumn{1}{c}{35675.0} & \multicolumn{1}{c}{41171.0} & \multicolumn{1}{c}{49315.0} & \multicolumn{1}{c}{60715.6} & \multicolumn{1}{c}{74386.4} & \multicolumn{1}{c}{87492.5} & \multicolumn{1}{c}{103983.0} & \multicolumn{1}{c}{102297.7} & \multicolumn{1}{c}{106130.6} \\
    Model (B) & \multicolumn{1}{c}{31387.3} & \multicolumn{1}{c}{35738.4} & \multicolumn{1}{c}{42535.8} & \multicolumn{1}{c}{52098.9} & \multicolumn{1}{c}{61343.7} & \multicolumn{1}{c}{74954.9} & \multicolumn{1}{c}{92758.6} & \multicolumn{1}{c}{95887.1} & \multicolumn{1}{c}{100155.4} \\
    Model (C) & \multicolumn{1}{c}{40808.1} & \multicolumn{1}{c}{45138.5} & \multicolumn{1}{c}{55214.8} & \multicolumn{1}{c}{69458.5} & \multicolumn{1}{c}{83958.6} & \multicolumn{1}{c}{100040.8} & \multicolumn{1}{c}{123592.1} & \multicolumn{1}{c}{129359.0} & \multicolumn{1}{c}{127399.2} \\ \hline
    \multicolumn{10}{l}{\textbf{Log-likelihood}}\\ \hline
    Model (A) & \multicolumn{1}{c}{-17530.5} & \multicolumn{1}{c}{-20253.5} & \multicolumn{1}{c}{-24315.5} & \multicolumn{1}{c}{-29977.8} & \multicolumn{1}{c}{-36811.2} & \multicolumn{1}{c}{-43341.3} & \multicolumn{1}{c}{-51648.5} & \multicolumn{1}{c}{-50746.8} & \multicolumn{1}{c}{-52690.3} \\
    Model (B) & \multicolumn{1}{c}{-15125.6} & \multicolumn{1}{c}{-17263.2} & \multicolumn{1}{c}{-20686.9} & \multicolumn{1}{c}{-25393.5} & \multicolumn{1}{c}{-30036.9} & \multicolumn{1}{c}{-36788.4} & \multicolumn{1}{c}{-45768.3} & \multicolumn{1}{c}{-47277.5} & \multicolumn{1}{c}{-49419.7} \\
    Model (C) & \multicolumn{1}{c}{-20074.1} & \multicolumn{1}{c}{-22217.2} & \multicolumn{1}{c}{-27251.4} & \multicolumn{1}{c}{-34355.3} & \multicolumn{1}{c}{-41634.3} & \multicolumn{1}{c}{-49625.4} & \multicolumn{1}{c}{-61533.0} & \multicolumn{1}{c}{-64339.5} & \multicolumn{1}{c}{-63316.6} \\ \hline
    \multicolumn{10}{l}{\textbf{Test LL} }\\ \hline
    Stat LL ratio (B vs A) & \multicolumn{1}{c}{4809.7} & \multicolumn{1}{c}{5980.6} & \multicolumn{1}{c}{7257.3} & \multicolumn{1}{c}{9168.7} & \multicolumn{1}{c}{13548.7} & \multicolumn{1}{c}{13105.7} & \multicolumn{1}{c}{11760.4} & \multicolumn{1}{c}{6938.6} & \multicolumn{1}{c}{6541.2} \\
    \textbackslash{}\# restrictions & \multicolumn{1}{c}{355} & \multicolumn{1}{c}{369} & \multicolumn{1}{c}{376} & \multicolumn{1}{c}{393} & \multicolumn{1}{c}{424} & \multicolumn{1}{c}{426} & \multicolumn{1}{c}{428} & \multicolumn{1}{c}{426} & \multicolumn{1}{c}{422} \\
    p-value & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} \\ \hline
    Stat LL ratio (B vs C) & \multicolumn{1}{c}{4948.4} & \multicolumn{1}{c}{4954.0} & \multicolumn{1}{c}{6564.5} & \multicolumn{1}{c}{8961.8} & \multicolumn{1}{c}{11597.4} & \multicolumn{1}{c}{12837.0} & \multicolumn{1}{c}{15764.7} & \multicolumn{1}{c}{17062.0} & \multicolumn{1}{c}{13896.9} \\
    \textbackslash{}\# restrictions & \multicolumn{1}{c}{355} & \multicolumn{1}{c}{369} & \multicolumn{1}{c}{376} & \multicolumn{1}{c}{393} & \multicolumn{1}{c}{424} & \multicolumn{1}{c}{426} & \multicolumn{1}{c}{428} & \multicolumn{1}{c}{426} & \multicolumn{1}{c}{422} \\
    p-value & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} \\ \hline \hline
\end{tabular}%
}
\end{table}%

\begin{landscape}
\begin{table}[htbp]
  \centering
  \footnotesize{
  \caption{Quality-of-fit diagnostic tests of the three models (Vessel, 3-digit level)}
    \label{tab:3models_diagnosis_vessel}%
   \begin{tabular}{l|c c c c c c c c c}
    \hline \hline
    \textbf{Year} & \multicolumn{1}{c}{\textbf{1974}} & \multicolumn{1}{c}{\textbf{1980}} & \multicolumn{1}{c}{\textbf{1985}} & \multicolumn{1}{c}{\textbf{1990}} & \multicolumn{1}{c}{\textbf{1995}} & \multicolumn{1}{c}{\textbf{2000}} & \multicolumn{1}{c}{\textbf{2005}} & \multicolumn{1}{c}{\textbf{2010}} & \multicolumn{1}{c}{\textbf{2013}} \\ \hline
    \multicolumn{10}{l}{\textbf{$R^2$}} \\ \hline
    Model (A) & 0.450 & 0.415 & 0.427 & 0.456 & 0.438 & 0.401 & 0.378 & 0.350 & 0.339 \\
    Model (B) & 0.612 & 0.575 & 0.571 & 0.590 & 0.611 & 0.571 & 0.541 & 0.491 & 0.462 \\
    Model (C ) & 0.424 & 0.401 & 0.374 & 0.429 & 0.456 & 0.431 & 0.417 & 0.358 & 0.349 \\ \hline
    \multicolumn{10}{l}{\textbf{SER} } \\ \hline
    Model (A) & 0.576 & 0.620 & 0.569 & 0.592 & 0.615 & 0.652 & 0.673 & 0.740 & 0.758 \\
    Model (B) & 0.484 & 0.528 & 0.493 & 0.514 & 0.512 & 0.551 & 0.578 & 0.656 & 0.684 \\
    Model (C) & 1.271 & 1.339 & 1.283 & 1.326 & 1.302 & 1.319 & 1.336 & 1.392 & 1.410 \\ \hline
    \multicolumn{10}{l}{\textbf{AIC criteria} } \\ \hline
    Model (A) & 33328.81 & 33010.27 & 40275.70 & 51142.62 & 60414.92 & 71365.89 & 85051.02 & 84789.89 & 88191.87 \\
    Model (B) & 27331.52 & 28067.31 & 34170.52 & 43664.74 & 49275.33 & 60475.91 & 73020.09 & 76161.33 & 80873.72 \\
    Model (C) & 46082.40 & 44370.26 & 58829.71 & 71461.52 & 77052.41 & 88746.51 & 103310.93 & 101166.91 & 104290.27 \\ \hline
    \multicolumn{10}{l}{\textbf{Log-likelihood}}\\ \hline
    Model (A) & -16287.40 & -16129.13 & -19767.85 & -25169.31 & -29790.46 & -35263.95 & -42122.51 & -41998.95 & -43692.93 \\
    Model (B) & -12985.76 & -13353.65 & -16398.26 & -21171.37 & -23905.66 & -29490.96 & -35844.04 & -37418.66 & -39751.86 \\
    Model (C) & -22674.20 & -21814.13 & -29045.86 & -35403.76 & -38125.20 & -43963.25 & -51245.46 & -50348.45 & -51783.14 \\ \hline
   \multicolumn{10}{l}{ \textbf{Test LL} } \\ \hline
    Stat LL ratio (B vs A) & 6603.28 & 5550.96 & 6739.18 & 7995.88 & 11769.59 & 11545.98 & 12556.94 & 9160.56 & 7882.15 \\
    $\#$ restrictions & 393   & 395   & 403   & 411   & 429   & 436   & 437   & 424   & 427 \\
    p-value & 0.00  & 0.00  & 0.00  & 0.00  & 0.00  & 0.00  & 0.00  & 0.00  & 0.00 \\ \hline
    Stat LL ratio (B vs C) & 19376,88 & 16920,95 & 25295,20 & 28464,79 & 28439,08 & 28944,59 & 30802,84 & 25859,58 & 24062,55 \\
    $\#$ restrictions & 393   & 395   & 403   & 411   & 429   & 436   & 437   & 424   & 427 \\
    p-value & 0.00  & 0.00  & 0.00  & 0.00  & 0.00  & 0.00  & 0.00  & 0.00  & 0.00 \\
\hline \hline
    \end{tabular}%
}
\end{table}%
\end{landscape}

@@

\subsection{Transport Cost Estimates: Yearly Detailed Results}
In this section, we complement Table 1 of the main text by reporting the year-to-year results of the estimation driven at the 3-digit classification level. Table \ref{tab_oa:result_air_ally3} reports the results for each year over 1974-2013 for air transport; Table \ref{tab_oa:result_vessel_ally3} reports similar results for vessel. In both cases, we report the estimated values of the transport costs (weighted mean and median) when only ad-valorem costs are modeled (Model (A)) and when both additive and ad-valorem costs are modeled (Model (B)).

\begin{landscape}
\begin{table}[htbp]
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
  %\centering
\caption{Air: Transport costs estimates, all years, 3-digit}
\begin{center}
\scalebox{0.85}{\begin{tabular}{lcccccccccccccccccccc}
\hline
\hline
Year  & 1974  & 1975  & 1976  & 1977  & 1978  & 1979  & 1980  & 1981  & 1982  & 1983  & 1984  & 1985  & 1986  & 1987  & 1988  & 1989  & 1990  & 1991  & 1992  & 1993 \\
\hline
\multicolumn{20}{l}{\textbf{Model (A) - With only Ad-Valorem Trade Costs} ($\widehat{\tau}^{ice}$, in \%)} \\
\hline
Mean  & 6.9   & 7.5   & 7.2   & 7.7   & 6.9   & 6.1   & 5.4   & 6.0   & 6.4   & 6.9   & 7.2   & 6.1   & 6.4   & 6.6   & 5.7   & 5.3   & 5.0   & 5.1   & 4.9   & 5.1 \\
Median & 5.4   & 6.4   & 6.9   & 7.1   & 6.3   & 5.3   & 3.8   & 4.9   & 5.3   & 6.1   & 6.7   & 5.5   & 5.9   & 6.3   & 5.3   & 4.6   & 4.4   & 4.5   & 4.5   & 4.4 \\
\hline
\multicolumn{20}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem Trade Costs} }\\ \hline
\multicolumn{20}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%)} }   \\
\hline
Mean  & 3.6   & 3.7   & 3.9   & 3.8   & 3.2   & 3.0   & 2.3   & 2.8   & 2.8   & 2.6   & 3.3   & 2.5   & 3.2   & 2.6   & 3.1   & 3.1   & 2.4   & 2.7   & 2.2   & 2.4 \\
Median & 2.7   & 2.7   & 2.9   & 2.7   & 2.1   & 2.4   & 1.6   & 1.8   & 1.9   & 1.9   & 2.7   & 1.8   & 2.1   & 2.0   & 2.0   & 1.9   & 1.6   & 1.5   & 1.5   & 1.6 \\

\hline
\multicolumn{20}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%)} }   \\
\hline
Mean  & 2.6   & 3.0   & 2.3   & 3.1   & 2.6   & 2.1   & 2.0   & 2.0   & 2.3   & 2.8   & 2.5   & 2.8   & 2.6   & 2.9   & 1.7   & 4.6   & 1.8   & 1.8   & 1.9   & 1.9 \\
Median & 1.1   & 1.2   & 0.9   & 1.3   & 1.1   & 0.7   & 0.5   & 0.6   & 0.8   & 1.0   & 1.0   & 1.3   & 1.3   & 1.5   & 1.0   & 0.7   & 0.8   & 0.6   & 0.9   & 0.8 \\
\hline
\# observations & 14955 & 15299 & 11397 & 10707 & 15222 & 15684 & 16118 & 16864 & 17322 & 18180 & 20644 & 19908 & 20695 & 20793 & 24663 & 25197 & 24958 & 25156 & 26191 & 28296 \\

%%%%%%%%%%%%%%%%2nd part of the table

\hline\hline
\multicolumn{20}{c}{ }  \\
\multicolumn{20}{c}{Continued}  \\
\hline\hline

Year  & 1994  & 1995  & 1996  & 1997  & 1998  & 1999  & 2000  & 2001  & 2002  & 2003  & 2004  & 2005  & 2006  & 2007  & 2008  & 2009  & 2010  & 2011  & 2012  & 2013 \\
\hline
\multicolumn{20}{l}{\textbf{Model (A) - With only Ad-Valorem Trade Costs} ($\widehat{\tau}^{ice}$, in \%)} \\
\hline
Mean  & 4.6   & 4.6   & 4.2   & 4.1   & 3.8   & 3.8   & 3.6   & 3.5   & 3.8   & 3.9   & 4.0   & 4.1   & 3.9   & 4.1   & 4.1   & 4.0   & 4.2   & 3.9   & 3.7   & 3.4 \\
Median & 3.7   & 3.8   & 3.1   & 3.0   & 2.7   & 2.8   & 2.5   & 2.4   & 2.7   & 2.6   & 2.9   & 3.1   & 2.7   & 3.0   & 3.2   & 3.0   & 3.4   & 3.1   & 3.0   & 2.9 \\
\hline
\multicolumn{20}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem Trade Costs} }\\ \hline
\multicolumn{20}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%)} }   \\
\hline
Mean  & 2.3   & 2.1   & 1.9   & 1.8   & 1.8   & 1.8   & 1.7   & 1.6   & 1.6   & 1.9   & 1.9   & 2.0   & 1.8   & 2.3   & 2.3   & 2.3   & 2.6   & 2.2   & 2.2   & 1.7 \\
Median & 1.3   & 1.4   & 1.4   & 1.3   & 1.3   & 1.5   & 1.2   & 1.1   & 1.2   & 1.4   & 1.4   & 1.6   & 1.4   & 1.9   & 1.9   & 1.8   & 2.2   & 1.7   & 1.9   & 1.7 \\
\hline
\multicolumn{20}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%)} }   \\
\hline
Mean  & 1.7   & 1.6   & 1.5   & 1.5   & 1.4   & 1.4   & 1.3   & 1.3   & 1.6   & 1.4   & 1.5   & 1.4   & 1.3   & 1.2   & 1.2   & 1.2   & 1.1   & 1.1   & 0.9   & 1.0 \\
Median & 0.8   & 0.7   & 0.6   & 0.6   & 0.5   & 0.5   & 0.5   & 0.5   & 0.5   & 0.5   & 0.6   & 0.5   & 0.5   & 0.5   & 0.5   & 0.5   & 0.4   & 0.4   & 0.4   & 0.5 \\
\hline
\# observations & 29948 & 31037 & 32187 & 33502 & 33492 & 33523 & 35027 & 34885 & 35159 & 35891 & 36990 & 41806 & 42554 & 40858 & 40159 & 38275 & 40279 & 41190 & 40909 & 39351 \\

\hline
\hline
\end{tabular}}%
	\end{center}
\end{table}%

>>>>

In this section, we report the estimation results of the three models: Model (A) (with only ad-valorem costs), Model (B) (with both additive and ad-valorem) and Model (C) (with only additive costs). Table \ref{tab:3models_estimation_results_air} reports the results for air transport, Table \ref{tab:3models_estimation_results_ves} for vessel transport.

@@

\begin{table}[htbp]
	\centering
	\footnotesize{
	\caption{Estimation results of the three models (Air, products at 5-digit level, sectors at 3-digit level)}
	\label{tab:3models_estimation_results_air}%
	\input{TableA1_air.tex}
   \begin{tablenotes}
	\tiny
	\item Statistics are weighted by value
	\item \textbf{Model (A): Iceberg transpost costs only}
	\item \textbf{Model (B): With additive and ad-valorem transport costs}
				\item \textbf{Model (C): With additive transport costs only}
\end{tablenotes}

@@

\begin{table}[htbp]
	\centering
	\footnotesize{
		\caption{Estimation results of the three models (Vessel, products at 5-digit level, sectors at 3-digit level)}
		\label{tab:3models_estimation_results_ves}%
		\input{TableA1_ves.tex}
		\begin{tablenotes}
			\tiny
		\item Statistics are weighted by value
		\item \textbf{Model (A): Iceberg transpost costs only}
		\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\item \textbf{Model (C): With additive transport costs only}
		\end{tablenotes}
   }
\end{table}%

@@

\begin{table}[htbp]
\centering
\footnotesize{
	\caption{Quality-of-fit diagnostic tests of the three models (Air, 3-digit level)}
	\label{tab:3models_diagnosis_air}%
	\input{TableA3_air.tex}
\begin{tablenotes}
	\tiny
	\item SER are weighted by value
	\item \textbf{Model (A): Iceberg transpost costs only}
	\item \textbf{Model (B): With additive and ad-valorem transport costs}
	\item \textbf{Model (C): With additive transport costs only}
\end{tablenotes}
}
\end{table}%

\begin{table}[htbp]
	\centering
	\footnotesize{
		\caption{Quality-of-fit diagnostic tests of the three models (Ves, 3-digit level)}
		\label{tab:3models_diagnosis_vessel}%
		\input{TableA3_ves.tex}
		\begin{tablenotes}
			\tiny
			\item SER are weighted by value
			\item \textbf{Model (A): Iceberg transpost costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
			\item \textbf{Model (C): With additive transport costs only}
\end{tablenotes}
}
\end{table}%

@@

\subsection{Transport Cost Estimates: Yearly Detailed Results}

In this section, we complement Table 1 of the main text by reporting the year-to-year results of the estimation driven at the 3-digit classification level. Table \ref{tab_oa:result_air_ally3} reports the results for each year over 1974-2013 for air transport; Table \ref{tab_oa:result_vessel_ally3} reports similar results for vessel. In both cases, we report the estimated values of the transport costs (weighted mean and median) when only ad-valorem costs are modeled (Model (A)) and when both additive and ad-valorem costs are modeled (Model (B)).

%JH : reprendre XXX ICI
\begin{landscape}
